%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\newcommand{\ts}{\textsuperscript}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{bibentry}
\usepackage{enumitem}

\name{Han-Yun(Henry) Yeh} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{(000)~$\cdot$~111~$\cdot$~1111 \\ john@smith.com} % Your phone number and email
\address{henryyeh034@gmail.com}
\address{github.com/henry034/}
\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf National Chiao Tung University} \hfill{Hsinchu, Taiwan} \hfill{\em Sep. 2016 - June 2019}
\begin{itemize} \item {M.S. in Communications Engineering (GPA: 4.02/4.3)} \end{itemize}
{\bf National Taipei University}\hspace*{2em} \hfill{Taipei, Taiwan} \hfill{\em Sep. 2012 - June 2016}
\begin{itemize} \item {B.S. in Communications Engineering (Rank: 1\ts{st}, GPA: 3.72/4.0 )} \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Hornors and awards SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Hornors and Awards}
    Academic
    \begin{rSubsection}{}{}{}{}
    \item {\bf Phi Tau Phi Award} (2016) - The Phi Tau Phi Scholastic Honor Society, Taipei Taiwan \\
    Award for top-ranked student in CE department among all classes
    \item {\bf Dean's List} (Fall '12, Fall '15) - NTPU CE Dept. - Taipe, Taiwan
    \item {\bf Scholarship} (2014) - Elytone Electronic CO., LTD. - Taipei, Taiwan
    \item {\bf Honerable Mention} (2014) - Taiwan National Collegiate Programming Contest - Taipei, Taiwan
    \item {\bf 29\ts{th} Place} (2014) - ACM ICPC Jarkarta Regional - Jarkarta Indonesia
    \end{rSubsection}
    
    Research
    \begin{rSubsection}{}{}{}{}
    \item {\bf 6\ts{th} Place} (2017) - IJCNLP Shared Task 2~[3] - Taipei, Taiwan
    \item {\bf Best Paper Award} (2014) - Oriental COCOSDA~[4] - Phuket, Thailand
    \item {\bf 1\ts{st} Place} (2015) - NTPU CE Senior Project Competition - Taipei, Taiwan
    \end{rSubsection}
    
    \end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experience}
    \begin{rSubsection}{National Chiao Tung University}{Hsinchu, Taiwan}{Graduate Student/Research Assistant, Speech Processing Lab}{Sep. 2016 - Jan. 2019}
        \item Research Topic: Chinese language model~[1]\\
        Experimented sequence labeling (TDNN+BLSTM, joint learning with word boundary prediction) and seq2seq (Transformer) model on Chinese pinyin to character problem. Reduced character error rate to 5.6\%.
        \item Dimensional sentiment analysis for Chinese phrases (DSAP)~[3] \\
        Achieved mean rank 6.5 among 24 submissions on Chinese phrases' valence and arousal prediction problem using modified word2vec and BLSTM model.
        \item Child Speech Impairment Supporting System\\
        Implemented corpus recording system (for speech impairment child) GUI using Java, in the cooperation project with NTU Hospital Hsinchu. Collected and analyzed about 200 childredn's sample.
        \item Managed information system and work station for research. \quad {\footnotesize *Arch Linux, Ubuntu...}
    \end{rSubsection}
    \begin{rSubsection}{National Taipei University}{Taipei, Taiwan}{Research Assistant, Speech and Multimedia Signal Processing Lab}{Sep. 2012 - June 2016}
        \item Senior project: {\em "An Automatic Grade Input System via Voice"}\\
        Constructed speech recognition system include voice activity detection and noise canceling (microphone array beamforming) module to enter student's name and score automatically. Obtained 1\ts{st} prize.
        \item Mandarin prosody generation~[2][4]\\
        Investigated the improvement of CRF-based base-phrase chunk feature and punctuation mark feature in Madarin text-to-speech system.
    \end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}
    \nobibliography{bib/mybib}
    \bibliographystyle{unsrt}
    
    \begin{enumerate}[label={[\arabic*]}]
    \item \bibentry{yeh2019}
    \item \bibentry{chiang2019punctuation}
    \item \bibentry{lee2017nctu}
    \item \bibentry{hung2014investigation}
    \end{enumerate}    
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
    \begin{rSubsection}{IBM, Inc}{Taipei, Taiwan}{Application Developer}{June 2018 - Oct. 2018}
        \item Organized health knowledge and designed decision tree for health information suggestion project using Python.
        \item Implemented backend processing for website user behavior statistics with Python, PHP, MongoDB, MySQL and depolyed service on AWS.
    \end{rSubsection}
    \begin{rSubsection2}{Application Developer Intern}{Jul. 2017 - Aug. 2017}
        \item Implemented AOI algorithm for defect detection using Python including OpenCV package.
    \end{rSubsection2}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Teaching and Advising Experience 
%----------------------------------------------------------------------------------------
\begin{rSection}{Teaching and Advising Experience}
    \begin{rSubsection}{Teaching Assistant, \it{National Chiao Tung University}}{Sep. 2016 - Jan. 2018}{}{HsinChu, Taiwan}
        \item "Principle of Microcomputer" course taught by Prof. Yi-Ru, Wang \hfill Sep. 2017 - Jan. 2018
        \item "Logic Design and Lab" course taught by Prof. Yi-Ru, Wang \hfill Sep. 2016 - Jan. 2017
    \end{rSubsection}
    \begin{rSubsection}{Teaching Assistant, \it{National Taipei University}}{Feb. 2015 - June 2016}{}{Taipei, Taiwan}
        \item "Physics Lab" course taught by Prof. Cheng-Yu, Chiang \hfill Feb. 2015 - June 2016
    \end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Activities
%----------------------------------------------------------------------------------------
\begin{rSection}{Activities}
    \begin{rSubsection}{2020 Formosa Grand Challenage}{Taipei, Taiwan}{Participant}{Nov. 2019 - Apr. 2020}
        \item Build model and labeled data to solve various Chinese reading comprehension task using Pytorh in the preliminary round. 
        Build rule-based dialog system to solve conversation problem with 20 diffierent domains in the final round.
    \end{rSubsection}
    \begin{rSubsection}{2018 5\ts{th} Pixnet Hackthon}{Taipei, Taiwan}{Participant}{Aug. 2018}
        \item Developed a device and management website for answering popular dishes using Google AIY Voice Kit and information from text mining on 200,000 Pixnet food blogs.
    \end{rSubsection}
    \begin{rSubsection}{NTPU CE Student Association}{Taipei, Taiwan}{Director of Information Management}{Sep. 2013 - June 2014}
        \item Managed student information system and designed advertising photo for promoting the activities of student association.
        \item Instructor of orientation events for freshman.
    \end{rSubsection}
    \begin{rSubsection2}{Leader of Curriculum-design Section}{Feb. 2015}
        \item Designed curriculum including IR remoter DIY, speaker/microphone DIY and PC building of 1\ts{st} NTPU CE winter camp.
    \end{rSubsection2}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, C, Java, PHP \\
Databases & MySQL, PostgreSQL \\
Frameworks & TensorFlow
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
