%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume_short} % Use the custom resume.cls style
\newcommand{\ts}{\textsuperscript}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{bibentry}
\usepackage{enumitem}
\usepackage{hyperref}
\name{Henry Yeh} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{(000)~$\cdot$~111~$\cdot$~1111 \\ john@smith.com} % Your phone number and email
\address{Santa Clara \\ \href{mailto:hanyuny@andrew.cmu.edu}{hanyuny@andrew.cmu.edu} \\ 341-314-7855}
\address{\href{https://linkedin.com/in/henry034}{linkedin.com/in/henry034} \\ \href{https://github.com/henry034}{github.com/henry034} \\ \href{https://henryyeh.cc}{henryyeh.cc}}
%\address{github.com/henry034/}
\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    \begin{rSubsection3}{ Carnegie Mellon University}{Mountain View, CA}{Feb. 2021 - Dec. 2022}
        \item {M.S. in Software Engineering} \\
        {\em Courses: Foundations of Software Engineering, Computer Systems, Software Verification and Testing}
    \end{rSubsection3}
    \begin{rSubsection3}{ National Chiao Tung University}{Hsinchu, Taiwan}{Sep. 2016 - June 2019}
        \item {M.S. in Communications Engineering (GPA: 4.02/4.3)} \\
        {\em Courses: Algorithms, Embedded Systems, Deep learning, Machine learning, Digital Speech Processing}
    \end{rSubsection3}
    \begin{rSubsection3}{ National Taipei University}{Taipei, Taiwan}{Sep. 2012 - June 2016}
        \item {B.S. in Communications Engineering (Rank: 1\ts{st}/33, GPA: 3.72/4.0 )} \\
        {\em Courses: Data structures, Network programming, Digital Signal Processing, Image Processing}
    \end{rSubsection3}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
    \begin{rSubsection3}{Schlumberger}{Digital Technology Intern}{May 2022 - Aug 2022}
        \item Deployed sample application on Kubernetes cluster, established pipeline to manage Docker and patch K8s, and integrated Observability tools including Grafana and Prometheus. Created tutorial to help developers migrating system and saved 50\% learning time $\star$ {\em DevOps, Kubernetes, Prometheus, Grafana}
    \end{rSubsection3}
    \begin{rSubsection3}{Novatek Microelectronics Corp.}{Software Firmware Engineer}{Aug 2020 - June 2021}
        \item Integrated IC verification report generator in C embedded programming for audio/digital signal processor (DSP) part of latest SmartTV System on Chip (SoC) IC, saved 50\% reporting time
        \item Optimized DTS sound effect algorithm in C embedded programming with Tensilia Hifi2/Hifi4 DSP processor, surpassed 4x speedup for audio processing
    \end{rSubsection3}
    \begin{rSubsection3}{IBM, Inc}{Application Developer/Intern}{June 2018 - Oct. 2018, Jul. 2017- Aug.2017}
        \item Designed a backend infrastructure to collect and analyze website users $\star$ {\em JavaScript, Python, PHP, MongoDB, MySQL, AWS}
        \item Implemented an automated optical inspection (AOI) algorithm to 
              detect defects in circuit board labels, increasing accuracy to 90\% $\star$ {\em Python, OpenCV}
    \end{rSubsection3}
\end{rSection}


%----------------------------------------------------------------------------------------
%	Project SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Course Project}
    \begin{list}{$\cdot$}{\leftmargin=1.5em}
        \itemsep -0.5em \vspace{-0.25em} % Compress items in list together for aesthetics
        \item {\bf Emergency Social Network} - Built a model view controller (MVC) structured web application using HTML5/CSS/JS with pug and Bootstrap for the front-end, Node.js with ExpressJS for the backend, MongoDB for the database and deployed on Heroku. 
        Experienced software engineering practices including scrum, design patterns, unit testing, CI/CD
    \end{list}
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experience}
    \begin{rSubsection3}{National Chiao Tung University}{RA @ Speech Processing Lab}{Sep. 2016 - Jan. 2019}
        \item Developed Long Short-term memory (LSTM)/Seq2Seq/Transformer based Mandarin language model, published as my master thesis, achieved 5.6\% character error rate (CER) \quad$\star$ {\em Speech processing, Deep learning, TensorFlow, Python}
        \item Quantified LSTM based Dimensional sentiment analysis for Chinese phrases, reached 6\ts{th} place \quad $\star$ {\em NLP, Python}
        \item Established Child Speech Impairment Supporting System UI, collected 5+ hours child corpus \quad $\star$ {\em Java}
    \end{rSubsection3}
    \begin{rSubsection3}{National Taipei University}{RA @ Signal Processing Lab}{Sep. 2012 - June 2016}
        \item Implemented Speech recognition system that featured energy-based voice activity detection and a beam-forming noise cancellation module to enter student’s grades automatically \quad$\star$ {\em C, HTK}
        \item Surveyed Mandarin prosody generation using CRF-based base-phrase chunk features and punctuation confidence for Mandarin text to speech system \quad$\star$ {\em C, CRF}
    \end{rSubsection3}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Hornors and awards SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Honors and Awards}
%    \begin{list}{$\cdot$}{\leftmargin=1.5em}
%        \itemsep -0.5em \vspace{-0.25em} % Compress items in list together for aesthetics
%        \item {\bf 6\ts{th} Place} (2017) - IJCNLP Shared Task 2: dimensional sentiment analysis for Chinese phrases
%        \item {\bf 1\ts{st} Place} (2015) - NTPU CE Senior Project Competition - Taipei, Taiwan
%        \item {\bf Best Paper Award} (2014) - Oriental COCOSDA: Proposed CRF-based models for prosody generation used in text-to-speech system - Phuket, Thailand
%    \end{list}
%\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C, Java, Javascript, PHP \\
Web Technologies & Bootstrap, jQuery, Nodejs (Express), SQL, NoSQL, Grafana, Prometheus \\
Frameworks and Tools & TensorFlow, PyTorch, OpenCV , Git, Vim, Kubernetes, Docker, Azure\\
\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------
%\begin{rSection}{Publications}
%    \nobibliography{bib/mybib}
%    \bibliographystyle{unsrt}
%    
%    \begin{enumerate}[label={[\arabic*]}]
%    \item \bibentry{yeh2019}
%    \item \bibentry{chiang2019punctuation}
%    \item \bibentry{lee2017nctu}
%    \item \bibentry{hung2014investigation}
%    \end{enumerate}    
%\end{rSection}



%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
